|

### 2023-02-03 paper.Rmd
Fri Feb  3 09:00:08 CET 2023: update-remote.sh

# bash /Users/rmn/masterThesis/eda-gp-2020/experiments/airfoil_1hl_maxIndSize_fullRun_30gens/re_evaluate_airfoil_1hl_maxIndSize_30gen.sh

# bash /Users/rmn/masterThesis/eda-gp-2020/experiments/airfoil_2hl_maxIndSize_fullRun_30gens/re_evaluate_airfoil_2hl_maxIndSize_30gen.sh

@@

# boston housing
bash /Users/rmn/masterThesis/eda-gp-2020/experiments/bostonHousing_2hl_maxIndSize_fullRun_30gens/re_evaluate_bostonHousing_2hl_maxIndSize_fullRun_30gens.sh

# concrete
bash /Users/rmn/masterThesis/eda-gp-2020/experiments/concrete_2hl_maxIndSize_fullRun_30gens/re_evaluate_concrete_2hl_maxIndSize_fullRun_30gens.sh

@@

@@

Another significant benefit of using pre-training in DAE-GP is that it is highly efficient in decreasing the number of training epochs that are necessary to train each generations DAE-LSTM model. Even though pre-training increased the median totalrun-time for the tested benchmark problem in combination with the chosen DAE-LSTM dimensions, reducing the number of training epochs might still be a possible way to lower the total

@@

The experiments conducted in this thesis did not find any significant benefits in using a pre-training strategy for using DAE-GP to solve real world symbolic regression problems.

>>>>

@@

# boston housing
bash /Users/rmn/masterThesis/eda-gp-2020/experiments/bostonHousing_2hl_150hn_fullRun_30gens/re_evaluate_bostonHousing_2hl_150hn_fullRun_30gens.sh

# concrete
bash /Users/rmn/masterThesis/eda-gp-2020/experiments/concrete_2hl_150hn_fullRun_30gens/re_evaluate_concrete_2hl_150hn_fullRun_30gens.sh

@@

<!-- add test results for statistical significance! -->

@@

Another significant benefit of using pre-training in DAE-GP is that it is highly efficient in decreasing the number of training epochs that are necessary to train each generations DAE-LSTM model. Even though pre-training increased the median total run-time for the tested benchmark problem in combination with the chosen DAE-LSTM dimensions, reducing the number of training epochs might be a possible way to lower the runtime of DAE-GP if further performance optimizations to the source code, especially during model sampling, can be achieved.

@@

The experiments conducted in this thesis did not find any significant benefits on both solution quality as well as run-time for solving pre-training strategy for using DAE-GP to solve real world symbolic regression problems.
